Supplementary material for\\ A Benchmark of Named Entity Recognition Approaches in Historical Documents\\ Application to 19$^{th}$ Century French Directories

### 2022-01-20 src-latex/parts/20-related-work.tex
Updates from Overleaf

\textbf{Tesseract} 4.1.1 (newest version: 5, released Nov. 2021)
\textbf{Pero OCR} version from git repo, master branch updated on Sep 15, 2021
\textbf{Kraken}

\textbf{Spacy} is a software library that offers NLP components assembled in modular pipelines specialised by language.
Although BERT is available in the latest version of SpaCy (v3), the pipeline for French does not provide a NER layer at the time of our experiments (jan. 2022).
Hence, we rely on SpaCy's ad hoc pipeline trained on French corpora and capable of named entity recognition.
% deep-sequoia and wikiner-fr, capable of named entity recognition.\textit{fr\_core\_news\_lg}\footnote{https://spacy.io/models/fr} trained two corpora in French: deep-sequoia and wikiner-fr, capable of named entity recognition.
The global architecture of these pipelines have not been yet published but are explained by the developers on their website.
Words are first encoded into local context-aware embeddings using a window-based CNN similar to~\cite{collobert2011}.
The decision layer is an adaptation of the transition-based model presented in~\cite{lample2016}.
As words are processed sequentially, their vectors are concatenated with those of the last known entities to encode the nearby predicted semantics.
The classification layer relies on a finite-state machine whose transition probabilities are learned using a multilayer perceptron.
% \bertrand{Drop the next sentences if we need space}
% In 2018~\cite{won2018} evaluated SpaCy's NER ability to detect place names in five corpora of ancient letters written in English.
% They measured an average F1 score of 0.57.
% The SpaCy developers claim an accuracy of 0.85 for the English NER pipeline \textit{en\_core\_web\_lg} on the OntoNotes 5.0 corpus\footnote{https://spacy.io/usage/facts-figures}.
%For our experiments, the French model \textit{fr\_core\_news\_lg} is fine-tuned using our ground truth corpus.

\textbf{Transformers / Bert / Hugging face}
Language model based on \textit{Transformers} \cite{vaswani2017attention}, like BERT \cite{devlin2018bert}, have become a new paradigm for NER\cite{li2020}. 
The learned embeddings can be used as distributed representations for input instead of traditional embeddings like Google Word2Vec, and they can be further fine-tuned for NER by adding an additional output layer. 
They can also be pretrained in an unsupervised way on historical texts for domain adaptation.
As the directories are written in French, we chose the language model CamemBERT \cite{martin-etal-2020-camembert}, a Transformer model trained on a French corpus.
\joseph{plutôt tourner ça pour dire qu'il existe des modèles FR / qu'on est limités par la dispo de modèles FR pré-entraînés ?}

\Cref{fig.protocol} depicts the evaluation protocol used to assess the OCR and NER systems.

\begin{figure}[tb]
    \includegraphics[width=\linewidth]{figs/protocol.pdf}
    \caption{Scheme of the evaluation protocol. \joseph{Missing "Ground truth" for NER stage?}}
    \label{fig.protocol}
    \end{figure}

>>>>

\textbf{Tesseract} 4.1.1 (newest version: 5, released Nov. 2021)

\textbf{Pero OCR} version from git repo, master branch updated on Sep 15, 2021

\textbf{Kraken}

\textbf{SpaCy} is a software library that offers NLP components assembled in modular pipelines specialised by language.
Although BERT is available in the latest version of SpaCy (v3), the pipeline for French does not provide a NER layer at the time of our experiments (jan. 2022).
Hence, we rely on SpaCy's ad hoc pipeline trained on French corpora and capable of named entity recognition.
% deep-sequoia and wikiner-fr, capable of named entity recognition.\textit{fr\_core\_news\_lg}\footnote{https://spacy.io/models/fr} trained two corpora in French: deep-sequoia and wikiner-fr, capable of named entity recognition.
The global architecture of these pipelines have not been yet published but are explained by the developers on their website.
Words are first encoded into local context-aware embeddings using a window-based CNN similar to~\cite{collobert2011}.
The decision layer is an adaptation of the transition-based model presented in~\cite{lample2016}.
As words are processed sequentially, their vectors are concatenated with those of the last known entities to encode the nearby predicted semantics.
The classification layer relies on a finite-state machine whose transition probabilities are learned using a multilayer perceptron.
% \bertrand{Drop the next sentences if we need space}
% In 2018~\cite{won2018} evaluated SpaCy's NER ability to detect place names in five corpora of ancient letters written in English.
% They measured an average F1 score of 0.57.
% The SpaCy developers claim an accuracy of 0.85 for the English NER pipeline \textit{en\_core\_web\_lg} on the OntoNotes 5.0 corpus\footnote{https://spacy.io/usage/facts-figures}.
%For our experiments, the French model \textit{fr\_core\_news\_lg} is fine-tuned using our ground truth corpus.

\textbf{CamemBERT}
Language model based on \textit{Transformers} \cite{vaswani2017attention}, like BERT \cite{devlin2018bert}, have become a new paradigm for NER\cite{li2020}. 
The learned embeddings can be used as distributed representations for input instead of traditional embeddings like Google Word2Vec, and they can be further fine-tuned for NER by adding an additional output layer. 
They can also be pretrained in an unsupervised way on historical texts for domain adaptation.
CamemBERT \cite{martin-etal-2020-camembert}, is a weel-known French language model derived from BERT, of which there are already trained versions for the NER task on the Hugging Face library.

The Figure \ref{fig.pipeline} depicts the evaluation protocol used to assess the combined performance of these OCR and NER systems.

### 2022-01-20 src-latex/parts/30-dataset.tex
MAJ Part 3
Updates from Overleaf

The directories to be processed are stored in different libraries in Paris\footnote{\textcolor{green}{Citer les bibliothèques sources?} \joseph{est-ce nécessaire ici ? Est-ce que ça peut être dans une annexe ?}\nathalie{Oui totalement...}}. They have been scanned independently and with various levels of quality. Moreover, they cover a wide period and have been produced by different publishers and printers. Therefore, their contents, indexes, layouts, methods of printing, etc. may vary a lot from one directory to another (see Figure \ref{fig:directories}).

@@

For training as testing purposes, our groundtruth dataset must be as representative as possible of the diversity of the available directories.

>>>>

The directories to be processed are stored in different libraries in Paris. They have been scanned independently and with various levels of quality. Moreover, they cover a wide period and have been produced by different publishers and printers. Therefore, their contents, indexes, layouts, methods of printing, etc. may vary a lot from one directory to another (see Figure \ref{fig:directories}).

@@

For training as testing purposes, our groundtruth dataset must be as representative as possible of the diversity of the available directories. The Table \ref{tab:directories} lists the directories selected, their layout, the structure of their entries, and the number of annotated entries according to the considered index.

### 2022-01-20 src-latex/parts/60-ner-xp2-pretraining-and-finetuning.tex
Updates from Overleaf

Each dataset is split into a training, a development and a test set following the exact same protocol as described in \cref{sec:ner-xp1-protocol}, except this time we do not need to create smaller training sets.
The train/dev/test sets are the same size for each NER set as they contain the same entries:

CmBERT and CmBERT+ptrn are fine-tuneon reference-gold and pero-gold to create two versions of each model: the former trained on manually corrected entries and the latter on OCR entries.
SpaCy NER is left aside as results from experiment 1 show that it is outperformed by BERT models.
Performance metrics are computed for each of the four resulting NER models against the test sets created from reference-gold, pero-gold and tesseract-gold.

Finally each is is split into a training, a dev and a test subset following the procedure presented in\cref{subsection:experiment-1-setup}.

\subsubsection{Huggingface CamemBERT}
\joseph{Copie de \cref{sub:ner-xp1-sysytems-huggingcam}. Je suggère de rédiger la section de l'XP 1 en premier et apporter précision nécessaires ici.}

Experiments 1 and 2 rely on the implementation of transformers provided by the software library Huggingface (transformers v.4.15.0, datasets v.1.17.0).
Our baseline CmBERT model is CamemBERT model published on the Hugging Face repository \footnote{\url{https://huggingface.co/Jean-Baptiste/camembert-ner}} and already trained for NER on wikiner-fr.
Its NER head is a linear model with a Softmax function.
CmBERT and CmBERT+ptrn are always fine-tuned using the same parameters, with at most 5000 training steps and an early stopping condition set to 3 evaluations in experiment 1 (5 in experiment 2) without improvement of the f1 score. Evaluations are performed every 100 steps.

\subsection{Protocol}

We fine-tune CmBERT and CmBERT+ptrn on reference-gold and pero-gold to create two versions of each model: the former trained on manually corrected entries and the latter on OCR entries.
SpaCy NER is left aside as results from experiment 1 show that it is outperformed by BERT models.
Performance metrics are computed for each of the four resulting NER models against the test sets created from reference-gold, pero-gold and tesseract-gold.

\subsection{Results and discussion}

CmBERT and CmBERT+ptrn are fine-tuned on the training sets from reference-gold (manually corrected entries) and pero-gold to produce 4 different models.
Their F1 score measured against the test tests from reference-gold, pero-gold and tesseract-gold are given in \cref{fig:exp_2_eval_ner}.
The results clearly show that models perform best when both the pre-training and the NER fine-tuning share the same characteristics (here, OCR noise) as the texts to be processed.

In our tests, pre-training the model brings a slight gain in performance ($\approx 0.5\%$).
We did not pre-train or fine-tune with texts extracted with Tesseract.
However, despite a loss of performance the model pre-trained and fine-tuned with pero-gold still gives the best results.
This is probably due to the fact that the texts produced by Pero-OCR feature characteristics intermediary between human transcriptions and Tesseract.

>>>>

Each dataset is split into a training, a development and a test set following the exact same protocol as described in \cref{sec:ner-xp1-protocol}, except this time we do not need to create smaller training sets.
As the NER sets contain 8341 entries, the producing train sets (resp. development and test) contain 6004 entries - 72\% of the total (resp. 668 - 8\% and 1669 - 20\%).

CmBERT and CmBERT+ptrn are fine-tuned on the training sets built from NER-reference and NER-pero.
Finally the metrics are measured against the three tests sets.

%\subsubsection{Huggingface CamemBERT}
%\joseph{Copie de \cref{sub:ner-xp1-sysytems-huggingcam}. Je suggère de rédiger la section de l'XP 1 en premier et apporter précision nécessaires ici.}

%Experiments 1 and 2 rely on the implementation of transformers provided by the software library Huggingface (transformers v.4.15.0, datasets v.1.17.0).
%Our baseline CmBERT model is CamemBERT model published on the Hugging Face repository \footnote{\url{https://huggingface.co/Jean-Baptiste/camembert-ner}} and already trained for NER on wikiner-fr.
%Its NER head is a linear model with a Softmax function.
%CmBERT and CmBERT+ptrn are always fine-tuned using the same parameters, with at most 5000 training steps and an early stopping condition set to 3 evaluations in experiment 1 (5 in experiment 2) without improvement of the f1 score. Evaluations are performed every 100 steps.

%\subsection{Protocol}

%We fine-tune CmBERT and CmBERT+ptrn on reference-gold and pero-gold to create two versions of each model: the former trained on manually corrected entries and the latter on OCR entries.
%SpaCy NER is left aside as results from experiment 1 show that it is outperformed by BERT models.
%Performance metrics are computed for each of the four resulting NER models against the test sets created from reference-gold, pero-gold and tesseract-gold.

\subsection{Results and discussion}
The measured F1-score are given in \cref{fig:exp_2_eval_ner}.
Results clearly show that models perform best when both the pre-training and the NER fine-tuning share the same characteristics (here, OCR noise) as the texts to be processed.

In our tests, pre-training the model brings a slight gain in performance ($\approx 0.5\%$).
We did not pre-train or fine-tune with texts extracted with Tesseract.
However, despite a loss of performance, the model pre-trained and fine-tuned on NER-pero still gives the best results.
This is probably due to the fact that the texts produced by Pero-OCR feature characteristics intermediary between human transcriptions and Tesseract.
This OCR tool removes the characted recognized with a low confidence, which is probably a great help to the NER.
